On the analytic structure of the linear response susceptibility in open systems

### 2018-05-04 AnalyticStructure_main.tex
update

The first element of this discussion is the introduction of the computational basis $\{\mu\}$ used to perform the DFT calculations subjacent to the LR analysis. This basis is composed by a 
finite set of elements (state something about the systematic character the basis? comment on the finite dimension of the computational domain?) that are chosen to ensure an unbiased description 
of the ground state properties of the system.

FIRST QUESTION: The usage of the $\{\mu\}$ basis allows us to obtain a reliable evaluation of the perturbation induced modification of an observable? 
The answer of this question is based on the analysis of equation \eqref{LinearResponseFunctDef2} and has been partially provided in section \ref{FluctuationState} (move that material in this section?). 
We can complete the answer by observing that $\ket{f_p(0)}$ can be obtained through a ground state calculation with the explicit time independent perturbation added to the system. So we can perform
a check on the goodness of the basis in this case as in a ground state calculation. Then use the localization argument of the fluctuation states to extend this reliability of the result up to
$\omega=|\eps_p|$.

SO TO SUMMARIZE: below the threshold the numerical convergence is regulated by the localization of the fluctuation states, in this range we can assess the reliability of the results provided by
the $\{\mu\}$ basis by looking at the basis-independence of the fluctuation states at $\omega=0$. Above the threshold the convergence can be reached due to the localized nature of 
$\bra{\psi_p}\op O$, in this case the computational setup provides reliable results if guarantees the unbiased reconstruction of fluctuation states in the support of $\bra{\psi_p}\op O$. 
In this range there is no a priori indicator of the goodness of the results.

@@

The previous considerations regard the relation between the localization properties of the fluctuation states and the possibility of having a quality indicator for the goodness of the $\{\mu\}$ 
basis. Now we aim to extend/reformulate the question of the numerical convergence to the case in which the excitation-based representation of the LR is adopted.

>>>>

The first element of this discussion is the introduction of the computational basis, made of $n_\mu$ basis functions $\{\mu\}$, used to perform the DFT calculations subjacent to the LR analysis. 
The properties of the $\mu$-basis (state something about the systematic character the basis? comment on the finite dimension of the computational domain?) are chosen to ensure an unbiased description 
of the ground state properties of the system.

FIRST QUESTION: The usage of the $\mu$-basis allows us to obtain a reliable evaluation of the perturbation induced modification of an observable? 
The answer of this question is based on the analysis of equation \eqref{LinearResponseFunctDef2} and has been partially provided in section \ref{FluctuationState} (move that material in this section?). 
We can complete the answer by observing that $\ket{f_p(0)}$ can be obtained through a ground state calculation with the explicit time independent perturbation added to the system. So we can perform
a check on the goodness of the basis in this case as in a ground state calculation. Then use the localization argument of the fluctuation states to extend this reliability of the result up to
$\omega=|\eps_p|$.

SO TO SUMMARIZE: below the threshold the numerical convergence is regulated by the localization of the fluctuation states, in this range we can assess the reliability of the results provided by
the $\mu$-basis by looking at the basis-independence of the fluctuation states at $\omega=0$. Above the threshold the convergence can be reached due to the localized nature of $\bra{\psi_p}\op O$, 
in this case the computational setup provides reliable results if it guarantees the unbiased reconstruction of fluctuation states in the support of $\bra{\psi_p}\op O$. In this range there is no a 
priori indicator of the goodness of the results.

@@

The previous considerations regard the relation between the localization properties of the fluctuation states and the possibility of having a quality indicator for the goodness of the $\mu$-basis. 
Now we aim to extend/reformulate the question of the numerical convergence to the case in which the excitation-based representation of the LR is adopted.
